Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box

### 2015-05-08 paper/paper 2/paper 2.tex
feedback Erman

\emph{Cardinality restrictions} can be expressed either generically (\textbf{\emph{generic constraints}}) by \emph{description logics (DL)} 
%and extensions  
or specifically (\textbf{\emph{specific constraints}}) by domain-specific constraint languages such as \emph{OWL 2}, \emph{DSP}, \emph{ShEx}, \emph{ReSh}, and \emph{SPIN}.
The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
For that reason, we map constraint types to \emph{DL} statements.

@@

%This paper aims to address two main \textbf{audiences}:
%(1) RDF data providers and consumers seeking how to ensure high data quality and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and  
%(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
The main \textbf{contributions} of this paper are:
(1) we provide a basic terminology and classification system for RDF constraints (section \ref{sec:vocabulary}),
(2) we developed a vocabulary to describe constraints of any RDF constraint type generically and specified its underlying semantics (section \ref{sec:vocabulary}),
(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (section \ref{sec:transformations}), and
(4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (section \ref{sec:validation}).
%(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)

@@

%The underlying \emph{semantics} for RDF validation is \emph{UNA} and \emph{CWA}.
RDF validation requires that different names represent different objects (\emph{\textbf{unique name assumption (UNA)}}), whereas,
\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
A data property is \emph{functional} (\emph{R-65}) if for each individual \emph{x}, there can be at most one distinct literal \emph{y} such that \emph{x} is connected by the data property to \emph{y}. 
When assuming \emph{UNA}, the functional property {\em title} (\ms{funct (title)}) causes a clash
in case the book {\em Huckleberry-Finn} has more than one \emph{title}.
%(\ms{title(Huckleberry-Finn,} \ms{The-Adventures-of-Huckleberry-Finn)}, \ms{title} \ms{(Huckleberry-Finn,} \ms{Die-Abenteuer-des-Huckleberry-Finn)}).
Assuming \emph{nUNA}, however, reasoning concludes that the titles {\em The-Adventures-of-Huckleberry-Finn} and {\em Die-Abenteuer-des-Huckleberry-Finn} are the same. 
%(\ms{\{The-Adventures-of-Huckleberry-Finn\}} = \ms{\{Die-Abenteuer-des-Huckle} \ms{berry-}\ms{Finn\}}).

Reasoning in \emph{OWL 2} is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
%which fits its primary design purpose to represent knowledge on the World Wide Web. 
%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
%\tb{the following example does not show the redundancy problem!}
%\tb{2. benefit: reasoning solves redundancy problem}
As each \emph{book} must have a \emph{title} (\ms{Book $\sqsubseteq \exists$ title.$\top$}) and {\em Hamlet} is a \emph{book} (\ms{Book(Hamlet)}),
{\em Hamlet} must have at least one \emph{title}.
In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know. 
On the other hand, RDF validation scenarios require the \emph{\textbf{closed-world assumption (CWA)}}, i.e., a statement is inferred to be false if it cannot be proved to be true.
When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
A constraint that says that a book must have at least one title in \emph{OWA}, 
does not mean that the title has to be unique. 
In every model  (an interpretation that makes a set of \emph{DL knowledge base} true), 
it can be the case that a book has a single title, however, 
this title is not unique. 
In some models it is \emph{The-Adventures-of-Huckleberry-Finn}, in others it is \emph{Die-Abenteuer-des-Huckleberry-Finn}. 
And since in every model there is only one, \emph{DL} sentences are satisfied. 
But this does not correspond to the intended constraint which is usual in \emph{CWA} way.   
%Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past. 
In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (\emph{CWA} and \emph{UNA}) as for RDF validation in general. 
%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
%\tb{feedback from Erman: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this. / Thomas: I think your issue is tackled now? No.}

@@

We recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as appendix of this paper) in which
we describe the intended behavior of each constraint type in terms of validation results depending on \emph{CWA} and \emph{UNA}.
If any two constraints are semantically the same (w.r.t. RDF semantics), they should detect the same set of violations regardless of RDF data, 
which means whenever the constraints are applied to any RDF data they point out the same violations.
To be able to define mappings between semantically equivalent \emph{specific constraints} (expressed by different languages) and 
between \emph{specific constraints} and \emph{generic constraints},
we show for each constraint type that their constraints lead to exactly the same violations which shows that they behave in the same way. 
We expressed constraint types by different languages
to document identical semantics for these languages with regard to appropriate constraint types.

@@

A \textbf{\emph{constraint language}} is a language which is used to formulate constraints.
The W3C Data Shapes working group defines \textbf{\emph{RDF constraint}} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
We identified four dimensions to classify constraint types:
\begin{itemize}
  \item \textbf{\emph{Universality:}} \emph{specific constraints} vs. \emph{generic constraints}
	\item \textbf{\emph{Complexity:}} \emph{simple constraints} vs. \emph{complex constraints}
	\item \textbf{\emph{Context:}} \emph{property constraints} vs. \emph{class constraints}
	\item \textbf{\emph{DL Expressivity:}} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
\end{itemize}

As there are already five promising constraint languages and our purpose is not to put a new constraint language, we rather developed a very simple lightweight vocabulary (only three classes, three object properties, and three data properties) which is universal enough to describe constraints of any constraint type expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
We call this vocabulary the \textbf{\emph{RDF Constraints Vocabulary (RDF-CV)}}\footnote{Available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.

@@

Constraints can be expressed either generically (\textbf{\emph{generic constraints}}) by the \emph{RDF-CV}   
or specifically (\textbf{\emph{specific constraints}}) by domain-specific constraint languages.
As the \emph{RDF-CV} describes constraints generically, the vocabulary does not distinguish constraints according to the dimension \emph{universality}. 
The majority of the constraint types can be expressed in \emph{DL}.
In contrast, there are certain constraint types which cannot be expressed in \emph{DL}, but are also expressible by the \emph{RDF-CV} . 
\textbf{\emph{Complex constraints}} encompass \textbf{\emph{simple constraints}} (atomic constraints) and/or further \emph{complex constraints},
i.e. \emph{DL} statements representing \emph{complex constraints} are created out of \emph{DL} statements standing for atomic and composed constraints (if expressible in \emph{DL}). 
Simple constraints may be applied to either properties (\textbf{\emph{property constraints}}) or classes (\textbf{\emph{class constraints}}).
The \emph{RDF-CV} does not contain any terms standing for \emph{simple} and \emph{complex constraints}, since \emph{context classes} of \emph{simple constraints} are just reused within \emph{complex constraints} (\emph{simple constraints} associated with \emph{context classes} must hold for individuals of these \emph{context classes}). 
%\tb{Erman: If you say its expressible in RDF-CV, than you impose that RDF-CV is a language rather than a vocabulary. "in different contexts they call it signature which is the same thing". Generally, a language uses vocabulary to construct sentences, and the set of those sentences, is the language.} (see section \ref{sec:evaluation})
As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to describe constraints of all possible constraint types.
\er{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}

@@

Sub-classes of \textbf{\emph{simple constraints}} are \textbf{\emph{property constraints}} and \textbf{\emph{class constraints}} (see the \emph{RDF-CV} implementation model in figure \ref{fig:RDF-CV-implementation-model}). 
For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
Lists of \emph{left} and \emph{right properties} can only be specified for \emph{property constraints}.

@@

A \emph{simple constraint} holds for all individuals of a \textbf{\emph{context class}}.
Consider, e.g., the following \emph{minimum qualified cardinality restriction} on the object property \emph{author}, which restricts \emph{publications} to have at least one \emph{author} which is a \emph{person}: 
\begin{DL}
$Publication \sqsubseteq \geq1 author . Person $
\end{DL}
The cardinality restriction is a constraint on the property \emph{author} and is therefore classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication} (see table \ref{tab:property-constraint-cardinality-restriction} for the mapping to \emph{RDF-CV}):

@@

The \textbf{\emph{constraining element}} indicates the actual type of constraint like \emph{DL} concept and role constructors, (in)equality, and further keywords for constraint types which cannot be expressed in \emph{DL} (e.g. regular expressions and constraining facets).
In some cases, a constraint is only complete when in addition to the \emph{constraining element} a \textbf{\emph{constraining value}} is stated.
The cardinality restriction 
\ms{$\geq$1 author.Person}, e.g., 
constructs an anonymous class of all individuals having at least one \emph{author} relationship to \emph{persons}.
The \emph{constraining element} of this \emph{property constraint} is the \emph{DL} at-least restriction \emph{$\geq$} and the \emph{constraining value} is \emph{1}.
\emph{Simple constraints} may refer to a list of \textbf{\emph{classes}}.
The qualified cardinality restriction above, e.g., refers to the class \emph{Person}, 
i.e. restricts the objects of the property \emph{author} to be of the class \emph{Person}.

For \emph{property constraints}, \textbf{\emph{left}} and \textbf{\emph{right property lists}} are specified.
The assignment of properties to these lists happens relative to the \emph{constraining element} - which may be an operator (e.g., $\sqsubseteq$ in case of \emph{object property paths}).
\emph{Object Property Paths} (\emph{R-55}; also called \emph{complex role inclusion axioms} in \emph{DL})
express that, if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
then \emph{x} is also related to \emph{y} by a particular object property. 
As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} (\ms{authorOf(Stephen-Hawking, A-Brief-History-Of-Time)}) whose \emph{genre} is \emph{Popular-Science} ({\ms{genre(A-Brief-History-Of-Time, Popular-Science)}),
the following \emph{object property path} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science} (\ms{authorOfGenre(Stephen-Hawking, Popular-Science)}):
\begin{DL}
authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre 
\end{DL}
Thus, when mapped to the \emph{RDF-CV} (see table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
and the property \emph{authorOfGenre} is on the right side:

@@

\textbf{\emph{Complex constraints}} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
\emph{Exclusive or} is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
The \emph{complex constraint} \emph{context-specific exclusive or of property groups} (\emph{R-13})
restricts individuals of given classes to have properties of only one of multiple mutually exclusive property groups.
\emph{Publications} are either identified by an \emph{ISBN} and a \emph{title} (for books) or by an \emph{ISSN} and a \emph{title} (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}, which can be expressed in \emph{ShEx} as follows:

>>>>

\emph{Cardinality restrictions} can be expressed either generically (\emph{generic constraints}) by \emph{description logics (DL)} 
%and extensions  
or specifically (\emph{specific constraints}) by domain-specific constraint languages such as \emph{OWL 2}, \emph{DSP}, \emph{ShEx}, \emph{ReSh}, and \emph{SPIN}.
The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
For that reason, we map constraint types to \emph{DL} statements.

@@

%This paper aims to address two main \textbf{audiences}:
%(1) RDF data providers and consumers seeking how to ensure high data quality and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and  
%(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
The main contributions of this paper are:
(1) we provide a basic terminology and classification system for RDF constraints (section \ref{sec:vocabulary}),
(2) we developed a vocabulary to describe constraints of any RDF constraint type generically and specified its underlying semantics (section \ref{sec:vocabulary}),
(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (section \ref{sec:transformations}), and
(4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (section \ref{sec:validation}).
%(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)

@@

%The underlying \emph{semantics} for RDF validation is \emph{UNA} and \emph{CWA}.
RDF validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
A data property is \emph{functional} (\emph{R-65}) if for each individual \emph{x}, there can be at most one distinct literal \emph{y} such that \emph{x} is connected by the data property to \emph{y}. 
When assuming \emph{UNA}, the functional property {\em title} (\ms{funct (title)}) causes a clash
in case the book {\em Huckleberry-Finn} has more than one \emph{title}.
%(\ms{title(Huckleberry-Finn,} \ms{The-Adventures-of-Huckleberry-Finn)}, \ms{title} \ms{(Huckleberry-Finn,} \ms{Die-Abenteuer-des-Huckleberry-Finn)}).
Assuming \emph{nUNA}, however, reasoning concludes that the titles {\em The-Adventures-of-Huckleberry-Finn} and {\em Die-Abenteuer-des-Huckleberry-Finn} are the same. 
%(\ms{\{The-Adventures-of-Huckleberry-Finn\}} = \ms{\{Die-Abenteuer-des-Huckle} \ms{berry-}\ms{Finn\}}).

Reasoning in \emph{OWL 2} is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
%which fits its primary design purpose to represent knowledge on the World Wide Web. 
%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
%\tb{the following example does not show the redundancy problem!}
%\tb{2. benefit: reasoning solves redundancy problem}
As each \emph{book} must have a \emph{title} (\ms{Book $\sqsubseteq \exists$ title.$\top$}) and {\em Hamlet} is a \emph{book} (\ms{Book(Hamlet)}),
{\em Hamlet} must have at least one \emph{title}.
In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know. 
On the other hand, RDF validation scenarios require the \emph{closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
A constraint that says that a book must have at least one title in \emph{OWA}, 
does not mean that the title has to be unique. 
In every model  (an interpretation that makes a set of \emph{DL knowledge base} true), 
it can be the case that a book has a single title, however, 
this title is not unique. 
In some models it is \emph{The-Adventures-of-Huckleberry-Finn}, in others it is \emph{Die-Abenteuer-des-Huckleberry-Finn}. 
And since in every model there is only one, \emph{DL} sentences are satisfied. 
But this does not correspond to the intended constraint which is usual in \emph{CWA} way.   
%Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past. 
In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (\emph{CWA} and \emph{UNA}) as for RDF validation in general. 
%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
%\tb{feedback from Erman: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this. / Thomas: I think your issue is tackled now? No.}

@@

We recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as appendix of this paper) in which
we describe the intended behavior of each constraint type in terms of validation results depending on \emph{CWA} and \emph{UNA}.
If any two constraints are semantically the same (w.r.t. RDF semantics), they should detect the same set of violations regardless of RDF data, 
which means whenever the constraints are applied to any RDF data they point out the same violations.
To be able to define mappings between semantically equivalent \emph{specific constraints} (expressed by different languages) and 
between \emph{specific constraints} and \emph{generic constraints},
we show for each constraint type that their constraints lead to exactly the same violations which shows that they behave in the same way. 
We express constraint types by different languages
to document identical semantics for these languages with regard to appropriate constraint types.

@@

A \emph{constraint language} is a language which is used to formulate constraints.
The W3C Data Shapes working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
We identified four dimensions to classify constraint types:
\begin{itemize}
  \item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
	\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
	\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
	\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
\end{itemize}

As there are already five promising constraint languages and our purpose is not to put a new constraint language, we rather developed a very simple lightweight vocabulary (only three classes, three object properties, and three data properties) which is universal enough to describe constraints of any constraint type expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.

@@

Constraints can be expressed either generically (\emph{generic constraints}) by the \emph{RDF-CV}   
or specifically (\emph{specific constraints}) by domain-specific constraint languages.
As the \emph{RDF-CV} describes constraints generically, the vocabulary does not distinguish constraints according to the dimension \emph{universality}. 
The majority of the constraint types can be expressed in \emph{DL}.
In contrast, there are certain constraint types which cannot be expressed in \emph{DL}, but are also expressible by the \emph{RDF-CV} . 
\emph{Complex constraints} encompass \emph{simple constraints} (atomic constraints) and/or further \emph{complex constraints},
i.e. \emph{DL} statements representing \emph{complex constraints} are created out of \emph{DL} statements standing for atomic and composed constraints (if expressible in \emph{DL}). 
Simple constraints may be applied to either properties (\emph{property constraints}) or classes (\emph{class constraints}).
The \emph{RDF-CV} does not contain any terms standing for \emph{simple} and \emph{complex constraints}, since \emph{context classes} of \emph{simple constraints} are just reused within \emph{complex constraints} (\emph{simple constraints} associated with \emph{context classes} must hold for individuals of these \emph{context classes}). 
%\tb{Erman: If you say its expressible in RDF-CV, than you impose that RDF-CV is a language rather than a vocabulary. "in different contexts they call it signature which is the same thing". Generally, a language uses vocabulary to construct sentences, and the set of those sentences, is the language.} (see section \ref{sec:evaluation})
As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to describe constraints of all possible constraint types.
\er{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}

@@

Sub-classes of \emph{simple constraints} are \emph{property constraints} and \emph{class constraints} (see the \emph{RDF-CV} implementation model in figure \ref{fig:RDF-CV-implementation-model}). 
For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
Lists of \emph{left} and \emph{right properties} can only be specified for \emph{property constraints}.

@@

A \emph{simple constraint} holds for all individuals of a \emph{context class}.
Consider, e.g., the following \emph{minimum qualified cardinality restriction} on the object property \emph{author}, which restricts \emph{publications} to have at least one \emph{author} which is a \emph{person}: 
\begin{DL}
$Publication \sqsubseteq \geq1 author . Person $
\end{DL}
The cardinality restriction is a constraint on the property \emph{author} and is therefore classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication} (see table \ref{tab:property-constraint-cardinality-restriction} for the mapping to \emph{RDF-CV}):

@@

The \emph{constraining element} indicates the actual type of constraint like \emph{DL} concept and role constructors, (in)equality, and further keywords for constraint types which cannot be expressed in \emph{DL} (e.g. regular expressions and constraining facets).
In some cases, a constraint is only complete when in addition to the \emph{constraining element} a \emph{constraining value} is stated.
The cardinality restriction 
\ms{$\geq$1 author.Person}, e.g., 
constructs an anonymous class of all individuals having at least one \emph{author} relationship to \emph{persons}.
The \emph{constraining element} of this \emph{property constraint} is the \emph{DL} at-least restriction \emph{$\geq$} and the \emph{constraining value} is \emph{1}.
\emph{Simple constraints} may refer to a list of \emph{classes}.
The qualified cardinality restriction above, e.g., refers to the class \emph{Person}, 
i.e. restricts the objects of the property \emph{author} to be of the class \emph{Person}.

For \emph{property constraints}, \emph{left} and \emph{right property lists} are specified.
The assignment of properties to these lists happens relative to the \emph{constraining element} - which may be an operator (e.g., $\sqsubseteq$ in case of \emph{object property paths}).
\emph{Object Property Paths} (\emph{R-55}; also called \emph{complex role inclusion axioms} in \emph{DL})
express that, if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
then \emph{x} is also related to \emph{y} by a particular object property. 
As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} (\ms{authorOf(Stephen-Hawking, A-Brief-History-Of-Time)}) whose \emph{genre} is \emph{Popular-Science} ({\ms{genre(A-Brief-History-Of-Time, Popular-Science)}),
the following \emph{object property path} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science} (\ms{authorOfGenre(Stephen-Hawking, Popular-Science)}):
\begin{DL}
authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre 
\end{DL}
Thus, when mapped to the \emph{RDF-CV} (see table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
and the property \emph{authorOfGenre} is on the right side:

@@

\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
\emph{Exclusive or} is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
The \emph{complex constraint} \emph{context-specific exclusive or of property groups} (\emph{R-13})
restricts individuals of given classes to have properties of only one of multiple mutually exclusive property groups.
\emph{Publications} are either identified by an \emph{ISBN} and a \emph{title} (for books) or by an \emph{ISSN} and a \emph{title} (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}, which can be expressed in \emph{ShEx} as follows:
